Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-07 doc/main_jfm.tex
adding some texts

The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
the initial circular shape  and the deformed configuration of the vesicle after a period of time. The tank-treading behavior appears after obtaining the equilibrium state. 
% needs to add more details about inclination angle, tank-treading frequency,...etc.
The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates. The reduced area is given by $A^* = 4\pi A/L^2$
where $A$ is the vesicle area and $L$ is the arc length of the vesicle.

@@

\begin{equation}
{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
\end{equation}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the initial vesicle midplane.

>>>>

The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
This vesicle consists of $58$ disks with radius $r=0.5$ and the tank-treading behavior appears after obtaining an equilibrium state. 
% needs to add more details about inclination angle, tank-treading frequency, repulsion, ...etc.
The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates. The reduced area is given by $A^* = 4\pi A/L^2$
where $A$ is the vesicle area and $L$ is the arc length of the vesicle.

@@

\begin{equation}
{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
\end{equation}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the initial vesicle midplane. Figure~\ref{figure6} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
